\plaintitle

### 2017-06-20 papers/IoT2017/analysis.tex
submission ready
updates

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading workflow.
%
First, we can show that the net amount of energy sold by prosumer $i$ for
each timestep is at most $\field{MAXEPA}_i$.  By definition, the
amount of energy sold is less than or equal to the amount of EPA
obtained by prosumer $i$.  A prosumer can obtain EPA either by
withdrawing from its smart meter or by purchasing form another
prosumer.  From its smart meter, prosumer $i$ can withdraw at most
$\field{MAXEPA}_i$.
Although the prosumer may also buy EPA from another prosumer, this
constitutes buying energy, which decreases the net amount of energy
sold with the same amount.
Hence, the net amount of energy sold by prosumer $i$ cannot exceed
$\field{MAXEPA}_i$.  By extending the argument, we can show that the net
amount of energy sold by a group of prosumers~$G$ cannot exceed
$\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, we can show that the net
amount of energy bought by a group of prosumers $G$ cannot exceed
$\sum_{i \in G} \field{MAXECA}_i$.

@@

\subsection{Privacy}
Due to our use of communication anonymity and mixing services, members
of a microgrid can observe only the amount of assets withdrawn by a
prosumer from its smart meter.
Since all trading transactions are anonymous, they do not reveal the
actual amount of assets traded by the prosumer.  If a prosumer has not traded away all of its assets, 
then it can also anonymously deposit the remainder to
a random address that was freshly generated by its smart meter. Note that even
if a prosumer does not wish to trade, it should always
withdraw, mix, and deposit the same amount of assets.  Otherwise, the
lack (or varying amount) of withdrawal would leak information.

>>>>

\subsection{Safety}
We now demonstrate that faulty or malicious prosumers cannot trade
excessive amounts of energy if normal prosumers follow the rules of
the trading workflow.  First, we can show that the net amount of
energy sold by prosumer $i$ for each timestep is at most
$\field{MAXEPA}_i$.  By definition, the amount of energy sold is less
than or equal to the amount of EPA obtained by prosumer $i$.

A prosumer can obtain EPA either by withdrawing from its smart meter
or by purchasing form another prosumer.  From its smart meter,
prosumer $i$ can withdraw at most $\field{MAXEPA}_i$.  Although the
prosumer may also buy EPA from another prosumer, this constitutes
buying energy, which decreases the net amount of energy sold with the
same amount.  Hence, the net amount of energy sold by prosumer $i$
cannot exceed $\field{MAXEPA}_i$.  By extending the argument, we can
show that the net amount of energy sold by a group of prosumers~$G$
cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, %we can
show that the net amount of energy bought by a group of prosumers $G$
cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

@@

\subsection{Privacy}
Due to our use of communication anonymity and mixing services, members
of a microgrid can observe only the amount of assets withdrawn by a
prosumer from its smart meter.  Since all trading transactions are
anonymous, they do not reveal the actual amount of assets traded by
the prosumer.  If a prosumer has not traded away all of its assets,
then it can also anonymously deposit the remainder to a random address
that was freshly generated by its smart meter. Even if a prosumer does
not wish to trade, it should always withdraw, mix, and deposit the
same amount of assets.  Otherwise, the lack (or varying amount) of
withdrawal would leak information.

### 2017-06-20 papers/IoT2017/concl.tex
updates

\section{Conclusion}
\label{sec:concl}

@@

This paper describes \change{how we address these challenges via}{\emph{Privacy-preserving Energy Transactions} (PETra),} an
innovative solution for anonymous energy trading within a transactive
microgrid.  PETra builds on distributed ledgers, such as
blockchains, and proven techniques for anonymity, such as mixing
services and onion routing.  We described the workflow of
anonymous energy trading and explained the novel transactions and
services used in PETra.  Finally, we discussed how PETra
 satisfies security, safety, and privacy requirements.  In
future work, we will provide rigorous proofs of satisfying these
requirements, and we will present an implementation of PETra with
performance results.

>>>>

\section{Concluding Remarks}
\label{sec:concl}

@@

This paper describes how we address these challenges via
\emph{Privacy-preserving Energy Transactions} (PETra), which is our
innovative solution for anonymous energy trading within a transactive
microgrid.  PETra builds on distributed ledgers, such as blockchains,
and proven techniques for anonymity, such as mixing services and onion
routing.  We described the workflow of anonymous energy trading and
explained the novel transactions and services used in PETra.  Finally,
we discussed how PETra satisfies security, safety, and privacy
requirements.  In future work, we will provide rigorous proofs of
satisfying these requirements, and we will present an implementation
of PETra with performance results.

### 2017-06-20 papers/IoT2017/related.tex
updates

Additionally, other approaches such as additional hardware components
are explored for potential privacy gains. Varodayan and Khisti study
using a rechargeable battery for partially protecting the privacy of
information contained in a household's electrical load
profile~\cite{varodayan2011smart}. They show that stochastic battery
policies may leak 26\% less information than a best-effort policy,
which holds the output load constant whenever possible. Tan et
al.\ study privacy in a smart metering system from an information
theoretic perspective in the presence of energy harvesting and storage
units~\cite{tan2013increasing}. They show that energy harvesting
provides increased privacy by diversifying the energy source, while a
storage device can be used to increase both energy efficiency and
privacy.
% They show that there exists a trade-off between the information
% leakage rate and the wasted energy rate, and study the impact of the
% energy harvesting rate and the size of the storage device on this trade-off.

PETra extends this earlier work by considering a decentralized
IoT system for transactive energy, and addressing the novel privacy
threat posed by trading. In particular, while earlier work
protected the prosumers' privacy from the DSO, we also protect it from
other prosumers as well as outside attackers.

A key element of our approach is the ability to distribute information
among peers via blockchains.  As blockchain technology develops and
matures, new frameworks, services, and protocols are being developed
to leverage the distributed ledgers provided by blockchains. For example, Hyperledger
Fabric is a platform for distributed ledger solutions, which was
designed to support pluggable implementations of different
components~\cite{hyperledger2017fabric}. 
%Bitcoin Lightning Network is
%decentralized system, in which transactions are sent over a network of
%micropayment channels, whose transfer of value occurs
%off-blockchain~\cite{poon2016bitcoin}. 
Since this paper focuses on
the theoretical foundations of PETra, any of these
distributed ledgers provide the required capabilities.

>>>>

Other approaches, such as additional hardware components, are explored
for potential privacy gains. Varodayan and Khisti study using a
rechargeable battery for partially protecting the privacy of
information contained in a household's electrical load
profile~\cite{varodayan2011smart}. They show that stochastic battery
policies may leak 26\% less information than a best-effort policy,
which holds the output load constant whenever possible. Tan et
al.\ study privacy in a smart metering system from an information
theoretic perspective in the presence of energy harvesting and storage
units~\cite{tan2013increasing}. They show that energy harvesting
provides increased privacy by diversifying the energy source, while a
storage device can be used to increase both energy efficiency and
privacy.
% They show that there exists a trade-off between the information
% leakage rate and the wasted energy rate, and study the impact of the
% energy harvesting rate and the size of the storage device on this trade-off.

PETra extends this earlier work by (1) leveraging a decentralized IoT
system for transactive energy and (2) addressing the novel privacy
threat posed by trading. In particular, while earlier work protected
the prosumers' privacy from the DSO, PETra also protects it from other
prosumers, as well as outside attackers.

A key element of PETra is its ability to distribute information among
peers via blockchains.  As blockchain technology develops and matures,
new frameworks, services, and protocols are being developed to
leverage the distributed ledgers provided by blockchains. For example,
Hyperledger Fabric is a platform for distributed ledger solutions,
which was designed to support pluggable implementations of different
components~\cite{hyperledger2017fabric}.
%Bitcoin Lightning Network is
%decentralized system, in which transactions are sent over a network of
%micropayment channels, whose transfer of value occurs
%off-blockchain~\cite{poon2016bitcoin}. 
Since this paper focuses on the theoretical foundations of PETra, any
of these distributed ledgers provide the required capabilities.

### 2017-06-20 papers/IoT2017/services.tex
updates

We now describe the various services that are provided in PETra.
Earlier, we discussed the distributed ledger, which permanently stores
valid transactions.  Below, we introduce the anonymous communication
service, the mixing service for transaction anonymity, the anonymous
bid storage, and smart-meter based billing.

@@

\subsubsection{Transaction Anonymity}
Communication anonymity is necessary, but not sufficient, for
anonymous trading. In particular, if prosumers used their own accounts
to transfer assets, their trades would not be anonymous.  Fortunately,
most distributed ledgers allow users to easily generate new addresses
at random, which are anonymous in the sense that no one can tell who
generated them.  However, if prosumers simply transferred assets to these
addresses, they could be easily de-anonymized by tracing the
assets back to the prosumers.

@@

A mixing service can be implemented using multiple approaches.  The
simplest one is to use a \emph{trusted third party}, called a
cryptocurrency tumbler, which can receive and send assets. However, anonymity
in this case depends on the trustworthiness and reliability
of the third party, who could easily de-anonymize the addresses.  A
more secure approach is to use decentralized protocols, such as
CoinShuffle~\cite{ruffing2014coinshuffle} or
Xim~\cite{bissias2014sybil}.  These protocols enable participants to
mix assets with each other, thereby eliminating the need for a trusted
third party.
Some newer cryptocurrencies, such as
Zerocoin~\cite{miers2013zerocoin}, provide built-in mixing services,
which are often based on cryptographic principles and proofs.

>>>>

We now describe the various services that are provided in PETra.
Earlier, we discussed PETra's distributed ledger, which permanently
stores valid transactions.  Below, we introduce the anonymous
communication service, the mixing service for transaction anonymity,
the anonymous bid storage, and smart-meter based billing.

@@

\subsubsection{Transaction Anonymity}
Communication anonymity is necessary, but not sufficient, for
anonymous trading. In particular, if prosumers used their own accounts
to transfer assets, their trades would not be anonymous.  Fortunately,
most distributed ledgers allow users to easily generate new addresses
at random, which are anonymous in the sense that no one can tell who
generated them.  If prosumers simply transferred assets to these
addresses, however, they could be easily de-anonymized by tracing the
assets back to the prosumers.

@@

A mixing service can be implemented using multiple approaches.  The
simplest one is to use a \emph{trusted third party}, called a
cryptocurrency tumbler, which can receive and send assets. Anonymity
in this case, however, depends on the trustworthiness and reliability
of the third party, who could easily de-anonymize the addresses.  A
more secure approach is to use decentralized protocols, such as
CoinShuffle~\cite{ruffing2014coinshuffle} or
Xim~\cite{bissias2014sybil}.  These protocols enable participants to
mix assets with each other, thereby eliminating the need for a trusted
third party.  Some newer cryptocurrencies, such as
Zerocoin~\cite{miers2013zerocoin}, provide built-in mixing services,
which are often based on cryptographic principles and proofs.

### 2017-06-20 papers/IoT2017/solution.tex
updates

This section describes Privacy-preserving Energy Transactions (PETra), our solution for providing privacy to prosumers
in a transactive energy IoT system, without compromising grid safety
and security.

\begin{figure*}[h]
\centering
\begin{tikzpicture}[x=3.8cm, y=1.6cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
\node[entity] (smartmeter) at (0, 1) {smart meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (1.9, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
\node[entity] (partner) at (3, 0) {other prosumer};
\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, above] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for clarity of presentation.}
\label{fig:sellFlow}
\end{figure*}

\subsection{Overview of the Trading Workflow}
We now provide a semi-formal description of the energy trading workflow
from the prosumers' perspective. 
Subsequent subsections will describe the assets, transactions, and services used for trading in more detail.

\subsubsection{Energy Selling Workflow}
Consider a prosumer who wishes to sell energy to another
prosumer, as shown in Figure~\ref{fig:sellFlow}\Abhishek{We need to mention what is the expected deadline by which this sequence of task should finish. }. 
As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.

@@

The prosumer can now engage in energy trading anonymously.  To find a
trade partner, it can either post an \emph{energy ask} on the bid
storage, or simply search the storage for an acceptable \emph{energy
  bid}.  To post an energy ask, the prosumer first proves to the
storage service---without revealing its original identity---that it
owns a production asset stored at an anonymous address. 
\Aron{This sentence was added because we removed the relevant safety requirement.}
Proving ownership prevents the prosumer from ``spamming'' the storage service with bogus asks.
The prosumer can then
post the energy ask \circled{4}, which contains an anonymous
communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference
to the production asset.  If another prosumer, who is seeking to buy energy,
finds the ask acceptable it can contact the seller using the
communication identifier included in the ask.

>>>>

This section describes \emph{Privacy-preserving Energy Transactions}
(PETra), which is our solution for providing privacy to prosumers in a
transactive energy IoT system, without compromising grid safety and
security.
\begin{figure*}[h]
\centering
\begin{tikzpicture}[x=3.8cm, y=1.6cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
\node[entity] (smartmeter) at (0, 1) {smart meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (1.9, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
\node[entity] (partner) at (3, 0) {other prosumer};
\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, above] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified Overview of the Flow of Assets from the Perspective of a Prosumer Who Sells Energy.}
\label{fig:sellFlow}
\end{figure*}

\subsection{Overview of the Trading Workflow}
We now provide a semi-formal description of the energy trading
workflow from the prosumers' perspective.  Subsequent subsections
describe the assets, transactions, and services used for trading in
more detail.

\subsubsection{Energy Selling Workflow}
Consider a prosumer who wishes to sell energy to another prosumer, as
shown in Figure~\ref{fig:sellFlow}\footnote{To prevent
  de-anonymization, a prosumer should use multiple addresses and
  multiple rounds of mixing, which we have omitted from the figure for
  clarity of presentation.}  \Abhishek{We need to mention what is the
  expected deadline by which this sequence of task should finish.}  As
its first step, the prosumer withdraws an \emph{energy production
  asset} from its smart meter.  An energy production asset represents
a permission to sell a certain amount of energy, and it is used to
enforce safety requirements.  If the prosumer has sufficient unsold
production capacity, the smart meter creates and transfers a
production asset to the prosumer using a \emph{smart meter
  transaction} \circled{1}, which is recorded on the distributed
ledger.

@@

The prosumer can now engage in energy trading anonymously.  To find a
trade partner, it can either post an \emph{energy ask} on the bid
storage, or simply search the storage for an acceptable \emph{energy
  bid}.  To post an energy ask, the prosumer first proves to the
storage service---without revealing its original identity---that it
owns a production asset stored at an anonymous address.  Proving
ownership prevents the prosumer from ``spamming'' the storage service
with bogus asks.  The prosumer can then post the energy ask
\circled{4}, which contains an anonymous communication
identifier\footnote{We discuss communication anonymity later.}, a
price, and a reference to the production asset.  If another prosumer,
who is seeking to buy energy, finds the ask acceptable it can contact
the seller using the communication identifier included in the ask.
